### 2017-05-02 paper/paper.tex
Fixed figure labeling order

\quad Once all reviews for a business were in one file, the script problems_over_time.py was used to analyze the reviews and graph the results. To accomplish this, each review in a <business_id>.json file with a star rating of 3 or fewer stars was tokenized, stemmed, and compared to the following list of words associated with traumatic narratives in Fig.4 on the left:

@@

\quad After importing the CSV version of the data into RapidMiner, we tested some basic visualization tools included with the package. For instance, in Figure 1 we created a histogram of the average star for a business versus the state in which it is located. Basic graphs like these can help refine our questions. For example, why does Illinois have significantly lower average stars than other states or provinces, even those that border it?

@@

\quad RapidMiner can also produce 3D scatterplots which is useful because we used latitude and longitude in conjunction with the city and state to locate businesses, since some of the business address data is missing and cannot be filled with default values or other common values used to replace missing data. Figure 2 depicts a graph of longitude vs. latitude vs. review count for businesses.

@@

\quad Much research has been done in recent years on Latent Semantic Analysis (or Indexing). This utilizes the fact that a given matrix?s Singular Value Decomposition provides us with a large degree of useful data concerning the nature of the matrix, namely which vectors and rows carry more weight as well as those with less impact. Furthermore, it provides a model through which new data can be projected onto the reduced subspace. The table below shows a sample of the reduced vector space and the first ten terms in each of the new topics.

@@

\quad The users dataset essentially provides a window into users' status, connections, and interactions within the Yelp ecosystem. The figure below shows a plot of the user density versus the average star rating. We see that the density grows around 3.25-4.25 stars with some traces of a bell curve regarding the number of reviews the user has written.

\begin{figure}[!h]
\includegraphics[width=0.45\textwidth, center]{u_reviews_vs_stars}
\end{figure}

@@

\quad To answer the question of what types of problems were repeatedly present in a business, we built a utility that analyzes the language found in reviews. As mentioned in the Related Work section, Jurafsky et al. (2014) used a log-odds-ratio informative Dirichlet prior to determine the 50 words most statistically overrepresented in Yelp reviews with one star. We then used the stemmed forms of most of these words (see Fig. 4 in Main Techniques, Natural Language Processing) to determine the “issue distribution” for a particular business during a particular month, two examples of which are below as Fig. 10:

@@

\quad Latitude and longitude are also significant to the category of a business. For businesses this is important because certain categories become abundant in certain areas. One example is that in both New York City and Montreal there are a significant number of creperies because of New York City’s large population density and Montreal’s French influences. New businesses should consider other locations where creperies aren’t as popular. This can provide opportunities for new or existing businesses to venture into new areas. It can also help reveal the niche in certain communities such as in Fig. 4 where certain areas have relatively high concentrations of fitness-related businesses and even martial arts. New businesses can add to concentrations of businesses with an extra twist or bring quality to a category. This quality can be better determined with the k-means clusters.

>>>>

\quad Once all reviews for a business were in one file, the script problems_over_time.py was used to analyze the reviews and graph the results. To accomplish this, each review in a <business_id>.json file with a star rating of 3 or fewer stars was tokenized, stemmed, and compared to the following list of words associated with traumatic narratives in Fig. 1 on the left:

@@

\quad After importing the CSV version of the data into RapidMiner, we tested some basic visualization tools included with the package. For instance, in Fig. 2 we created a histogram of the average star for a business versus the state in which it is located. Basic graphs like these can help refine our questions. For example, why does Illinois have significantly lower average stars than other states or provinces, even those that border it?

@@

\quad RapidMiner can also produce 3D scatterplots which is useful because we used latitude and longitude in conjunction with the city and state to locate businesses, since some of the business address data is missing and cannot be filled with default values or other common values used to replace missing data. Fig. 3 depicts a graph of longitude vs. latitude vs. review count for businesses.

@@

\quad Much research has been done in recent years on Latent Semantic Analysis (or Indexing). This utilizes the fact that a given matrix?s Singular Value Decomposition provides us with a large degree of useful data concerning the nature of the matrix, namely which vectors and rows carry more weight as well as those with less impact. Furthermore, it provides a model through which new data can be projected onto the reduced subspace. The table below as Fig. 4 shows a sample of the reduced vector space and the first ten terms in each of the new topics.

@@

@@

\quad To answer the question of what types of problems were repeatedly present in a business, we built a utility that analyzes the language found in reviews. As mentioned in the Related Work section, Jurafsky et al. (2014) used a log-odds-ratio informative Dirichlet prior to determine the 50 words most statistically overrepresented in Yelp reviews with one star. We then used the stemmed forms of most of these words (see Fig. 1 in Main Techniques, Natural Language Processing) to determine the “issue distribution” for a particular business during a particular month, two examples of which are below as Fig. 10:

@@

\quad Latitude and longitude are also significant to the category of a business. For businesses this is important because certain categories become abundant in certain areas. One example is that in both New York City and Montreal there are a significant number of creperies because of New York City’s large population density and Montreal’s French influences. New businesses should consider other locations where creperies aren’t as popular. This can provide opportunities for new or existing businesses to venture into new areas. It can also help reveal the niche in certain communities such as in Fig. 5 where certain areas have relatively high concentrations of fitness-related businesses and even martial arts. New businesses can add to concentrations of businesses with an extra twist or bring quality to a category. This quality can be better determined with the k-means clusters.
